\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor,sectsty}
\definecolor{astral}{RGB}{46,116,181}

%opening
\title{\color{astral}A\color{black}rtifical \color{astral}M\color{black}usical \color{astral}I\color{black}ntelligence}
\author{Juan Fernández-Gracia}

\begin{document}

\maketitle

\begin{abstract}
This document describes a project for a machine learning/artificial intelligence based generation of music. It will rely mostly on developed projects and try to connect them to create \color{astral}AM.I.\color{black} With this project I want to create a platform that creates an ecology of musicians that create all of the products associated to music but everything through artificial intelligence.
\end{abstract}

\section{Introduction}

Artificial intelligence and machine learning techniques are getting to a point where they are able to do tasks that traditionally were thought to be only accessible to humans because they involve skills that are difficult to implement computationally such as intuition or creativity. Projects like AlphaGo have shown that intuition can be somehow encoded into a machine, at least for a particular game. 

\section{Thinking big}



\section{The protopype}

Automated generation of music, covers, band name, lyrics, choosing genre, videoclips, partiture, musicians (with all their characteristics)... from an stimulus (words, images, or any kind of data).

\section{Timeline}

\section{Resources}

\begin{itemize}
 \item Musegan, very interesting music generation: https://salu133445.github.io/musegan/ (part of openAI https://openai.com/)
 \item GPT-2, the Language model that shocked the world with its entirely fictitious story about the unicorns inhabiting a secret South American valley. https://github.com/openai/gpt-2
 \item Pat Savage look at the papers! https://patrickesavage.wordpress.com/
 \item Independent component analysis. (separate streams for guitar etc)
 \item Not open source:
 \begin{itemize}
  \item https://filmora.wondershare.com/audio-editing/best-ai-music-composer.html
  \item https://algorhythm.ai/
  \item https://www.aiva.ai/
 \end{itemize}
 \item Artists https://aiartists.org/ai-generated-art-tools
 \item https://www.thispersondoesnotexist.com/ https://github.com/NVlabs/stylegan2
 \item free stuff https://icons8.com/
 \item more free stuff https://archive.org/
 \item All the melodies that can exist https://github.com/allthemusicllc
\end{itemize}

\bibliography{AMI}

\end{document}
